{\bf {\Large Title....}}

### 2016-07-30 ident_manu.tex
ident tables added

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Sat Jul 30 12:31:08 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist}).  For the first selection heuristic, all sensitive parameters from the optics ($n = $ $4$, $\gamma =$  $3.7$) and organic matter ($n = $ $7$, $\gamma =$  $1.7$) categories were selected, whereas 23 were selected for phytoplankton ($\gamma = $ $13.7$), five for temperature ($\gamma = $ $11.4$), and five for zooplankton ($\gamma = $ $3.1$).  For the second selection heuristic, 20 parameters were selected ($\gamma = $ $4.6$, with a majority from the phytoplankton category).  For the third heuristic, 18 parameters were selected ($\gamma = $ $9.2$) with equal representation between categories. For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.  Selection independent of category showed that including \textit{KNO3} caused in increase in $\gamma$ from $4.6$ to $15.6$ and equal selection within cateogies showed that including \textit{Tref(nospA+nospZ)$_{p2}$} caused in increase in $\gamma$ from $9.2$ to $66.2$.  Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts}).  Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.  Interestingly, no parameters from the temperature category were selected.

@@

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters with three different heuristics. Parameters are selected by decreasing sensitivity for all examples (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}). The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c). Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\gamma > 15$ or if the maximum number of possible parameters is selected.}\label{fig:heurist}
\end{figure}

@@

\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for selected state variables. Parameters are selected by decreasing sensitivity indepent of parameter categories. Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\gamma > 15$.}\label{fig:heurist_stts}
\end{figure}

>>>>

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Sat Jul 30 12:41:03 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

Each of the three selection heuristics (blocked by parameter category, independent of category, all categories equally) for \ac{do} differed in the number of selected parameters and distribution of parameters within each category (if applicable, \cref{fig:heurist,tab:identall1}).  For the first selection heuristic, all sensitive parameters from the optics ($n = $ $4$, $\gamma =$  $3.7$) and organic matter ($n = $ $7$, $\gamma =$  $1.7$) categories were selected, whereas 23 were selected for phytoplankton ($\gamma = $ $13.7$), five for temperature ($\gamma = $ $11.4$), and five for zooplankton ($\gamma = $ $3.1$).  For the second selection heuristic, 20 parameters were selected ($\gamma = $ $4.6$, with a majority from the phytoplankton category, \cref{tab:identall1}).  For the third heuristic, 18 parameters were selected ($\gamma = $ $9.2$) with equal representation between categories. For the second and third selection heuristics, an individual parameter caused a disproportianate increase in $\gamma$ that forced the selection to stop.  Selection independent of category showed that including \textit{KNO3} caused in increase in $\gamma$ from $4.6$ to $15.6$ and equal selection within cateogies showed that including \textit{Tref(nospA+nospZ)$_{p2}$} caused in increase in $\gamma$ from $9.2$ to $66.2$.  Finally, parameter selection for other state variables (\ac{chla}, \ac{par}, nitrate, ammonium, particulate organic matter, dissolved organic matter, phosphorus) also showed that a limited number of parameters were identifiable (for brevity, only results using the second set of selection heuristics are shown, \cref{fig:heurist_stts,tab:identall2}).  Less than ten parameters were selected for each of the remaining state variables with most selected from the phytoplankton category.  Interestingly, no parameters from the temperature category were selected.

@@

% ident all states
%latex.default(identall1, file = "", rowlabel = "Parameter description",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:identall1", rowname = descrip, colheads = colnms,     rgroupTexCmd = NULL)%
\begin{table}[!tbp]
{\footnotesize
\caption{Parameter identifiability for dissolved oxygen.  Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\gamma < 15$.  Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:identall1}} 
\begin{center}
\begin{tabular}{lllll}
\hline\hline
\multicolumn{1}{l}{Parameter description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
\hline
\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$1$\textsuperscript{P}&$328.35$&$1$\tabularnewline
\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$2$\textsuperscript{P}&$232.8$&$1$\tabularnewline
\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p5}$}}&$3$\textsuperscript{P}&$7.57$&$1$\tabularnewline
\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p2}$}}&$4$\textsuperscript{P}&$4.08$&$1$\tabularnewline
\scriptsize{phytoplankton basal respiration coefficient}&\scriptsize{\textit{respb$_{p4}$}}&$5$\textsuperscript{P}&$3.1$&$1$\tabularnewline
\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$6$\textsuperscript{P}&$2.98$&$1.01$\tabularnewline
\scriptsize{Tref(nospA+nospZ): Optimum temperature for growth(C)}&\scriptsize{\textit{Tref(nospA+nospZ)$_{p4}$}}&$1$\textsuperscript{T}&$2.9$&$1.02$\tabularnewline
\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p4}$}}&$7$\textsuperscript{P}&$2.88$&$1.04$\tabularnewline
\scriptsize{coefficient for non-limiting nutrient}&\scriptsize{\textit{aN$_{p1}$}}&$8$\textsuperscript{P}&$2.7$&$1.05$\tabularnewline
\scriptsize{P-uptake rate measured at umax}&\scriptsize{\textit{vmaxP$_{p3}$}}&$9$\textsuperscript{P}&$2.23$&$1.07$\tabularnewline
\scriptsize{phytoplankton basal respiration coefficient}&\scriptsize{\textit{respb$_{p3}$}}&$10$\textsuperscript{P}&$2.15$&$1.73$\tabularnewline
\scriptsize{rate constant for nitrification}&\scriptsize{\textit{k11}}&$1$\textsuperscript{OM}&$2.11$&$1.73$\tabularnewline
\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p3}$}}&$11$\textsuperscript{P}&$1.99$&$1.73$\tabularnewline
\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$1.91$&$1.73$\tabularnewline
\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$1.64$&$1.77$\tabularnewline
\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$12$\textsuperscript{P}&$1.61$&$4.1$\tabularnewline
\scriptsize{minimum N cell-quota}&\scriptsize{\textit{QminN$_{p3}$}}&$13$\textsuperscript{P}&$1.53$&$4.1$\tabularnewline
\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$3$\textsuperscript{OM}&$1.49$&$4.2$\tabularnewline
\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$4$\textsuperscript{OM}&$1.37$&$4.62$\tabularnewline
\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p4}$}}&$14$\textsuperscript{P}&$1.35$&$4.62$\tabularnewline
\hline
\end{tabular}\end{center}}

% ident all states
%latex.default(identall2, file = "", rowlabel = "State variable, parameter description",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:identall2", rgroup = unique(as.character(stts)),     n.rgroup = as.numeric(table(as.character(stts))), rowname = descrip,     colheads = colnms, rgroupTexCmd = NULL)%
\begin{table}[!tbp]
{\footnotesize
\caption{Parameter identifiability for ammonium, chlorophyll, irradiance, nitrate, OM1, OM2, and phosphate.  Selection followed the second heuristic where parameters were selected by decreasing sensitivity up to maximum $\gamma < 15$.  Rank describes the parameter sensitivity in each category (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:identall2}} 
\begin{center}
\begin{tabular}{lllll}
\hline\hline
\multicolumn{1}{l}{State variable, parameter description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
\hline
{Ammonium}&&&&\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$2.38$&$1$\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$2.23$&$3.1$\tabularnewline
~~\scriptsize{rate constant for nitrification}&\scriptsize{\textit{k11}}&$1$\textsuperscript{OM}&$0.68$&$3.1$\tabularnewline
~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$0.46$&$3.12$\tabularnewline
~~\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$3$\textsuperscript{OM}&$0.39$&$6.53$\tabularnewline
~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$3$\textsuperscript{P}&$0.35$&$7.18$\tabularnewline
~~\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p4}$}}&$4$\textsuperscript{P}&$0.35$&$7.26$\tabularnewline
~~\scriptsize{N-uptake rate measured at umax}&\scriptsize{\textit{vmaxN$_{p3}$}}&$5$\textsuperscript{P}&$0.34$&$13.14$\tabularnewline
\hline
{Chlorophyll}&&&&\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$104.26$&$1$\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$47.86$&$3.65$\tabularnewline
~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$3$\textsuperscript{P}&$1.71$&$4.07$\tabularnewline
~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$1$\textsuperscript{OM}&$1.29$&$5.58$\tabularnewline
\hline
{Irradiance}&&&&\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$0.32$&$1$\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$0.25$&$4.87$\tabularnewline
~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p3}$}}&$3$\textsuperscript{P}&$0.19$&$5.38$\tabularnewline
~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$4$\textsuperscript{P}&$0.17$&$7.61$\tabularnewline
~~\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$0.15$&$13.34$\tabularnewline
~~\scriptsize{phytoplankton basal respiration coefficient}&\scriptsize{\textit{respb$_{p3}$}}&$5$\textsuperscript{P}&$0.11$&$13.5$\tabularnewline
~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$1$\textsuperscript{OM}&$0.08$&$14.64$\tabularnewline
\hline
{Nitrate}&&&&\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$1.07\times 10^{38}$&$1$\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$1.44\times 10^{23}$&$1$\tabularnewline
~~\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$2\times 10^{5}$&$10.55$\tabularnewline
\hline
{OM1}&&&&\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1.5$\textsuperscript{P}&$1.13$&$1$\tabularnewline
~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p4}$}}&$1.5$\textsuperscript{P}&$0.78$&$1.68$\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$3$\textsuperscript{P}&$0.76$&$8.66$\tabularnewline
~~\scriptsize{turnover rate for OM1A and OM1G}&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$0.71$&$8.98$\tabularnewline
~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$4$\textsuperscript{P}&$0.48$&$9.22$\tabularnewline
~~\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$0.43$&$9.22$\tabularnewline
\hline
{OM2}&&&&\tabularnewline
~~\scriptsize{turnover rate for OM2A and OM2G}&\scriptsize{\textit{KG2}}&$1$\textsuperscript{OM}&$1.3$&$1$\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$1$\textsuperscript{P}&$0.94$&$2.01$\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p1}$}}&$2$\textsuperscript{P}&$0.74$&$7.65$\tabularnewline
~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p4}$}}&$3$\textsuperscript{P}&$0.35$&$11$\tabularnewline
~~\scriptsize{O2 concentration that inhibits denitrification}&\scriptsize{\textit{KstarO2}}&$2$\textsuperscript{OM}&$0.34$&$11.29$\tabularnewline
~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p3}$}}&$4$\textsuperscript{P}&$0.31$&$11.44$\tabularnewline
~~\scriptsize{Chla specific absorption at 490 nm}&\scriptsize{\textit{astar490}}&$1$\textsuperscript{O}&$0.29$&$11.54$\tabularnewline
~~\scriptsize{maximum growth rate of zooplankton}&\scriptsize{\textit{Zumax$_{z1}$}}&$1$\textsuperscript{Z}&$0.29$&$11.66$\tabularnewline
\hline
{Phosphate}&&&&\tabularnewline
~~\scriptsize{initial slope of the photosynthesis-irradiance relationship}&\scriptsize{\textit{alpha$_{p3}$}}&$1$\textsuperscript{P}&$2.92$&$1$\tabularnewline
~~\scriptsize{P-uptake rate measured at umax}&\scriptsize{\textit{vmaxP$_{p3}$}}&$2$\textsuperscript{P}&$1.57$&$2.23$\tabularnewline
~~\scriptsize{mortality coefficient}&\scriptsize{\textit{mA$_{p3}$}}&$3$\textsuperscript{P}&$0.78$&$2.57$\tabularnewline
~~\scriptsize{phytoplankton carbon/cell}&\scriptsize{\textit{Qc$_{p3}$}}&$4$\textsuperscript{P}&$0.73$&$5.29$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters with three different heuristics. Parameters are selected by decreasing sensitivity for all examples (\cref{tab:optsens,tab:tempsens,tab:phytosens,tab:zoopsens,tab:omsens}). The parameter selecions are blocked within each category (a), independent of category (b), or considering all categories equally (c). Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\gamma > 15$ or if the maximum number of possible parameters is selected. See \cref{tab:identall1} for values in (b).}\label{fig:heurist}
\end{figure}

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) of selecting parameters for selected state variables. Parameters are selected by decreasing sensitivity indepent of parameter categories. Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\gamma > 15$.  See \cref{tab:identall2} for values.}\label{fig:heurist_stts}
\end{figure}
